Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-06-04 Thesis/chapter/03-theoretical-background.tex
ir?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning}
\subsubsection{History}
find cool examples like in https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a
noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
See protocoll
dall-e 2 \cite{Marcus2022}
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsubsection{Particle Swarm Optimization}
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
\subsubsection{Linear Regression}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistics, Regressin and Machine Learning}
\subsubsection{History}
find cool examples like in \url{https://pubs.rsc.org/en/content/articlehtml/2019/sc/c9sc01742a}  \\
\url{https://medium.com/@LightOnIO/beyond-overfitting-and-beyond-silicon-the-double-descent-curve-18b6d9810e1b}  \\
\url{https://www.nature.com/articles/427297a}\\
\url{https://www.sciencedirect.com/science/article/abs/pii/S0040609001015164} \\
\url{https://ieeexplore.ieee.org/abstract/document/6656789}\\
\url{https://www.sciencedirect.com/science/article/abs/pii/S0038092X04000854}\\
\url{https://www.sciencedirect.com/science/article/abs/pii/S007964251930101X}\\

noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
See protocoll
Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
dall-e 2 \cite{Marcus2022}\\
vNeumann 4 param elephant \cite{Dyson2004}\\
4 param elephant \cite{Mayer2010}\\
"All models are wrong but some are useful" \cite{Box1979}\\
"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
\subsubsection{Design of Experiment}
\subsubsection{Particle Swarm Optimization}
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
\subsubsection{Linear Regression}
